Classless Java: Tuning Java Interfaces

### 2015-12-02 paper/sections/Appendix.tex
Revise formalization and proof.

\subsection{THEOREM}\label{subsec:theorem}

\textbf{THEOREM. }
For a given $\II_0\ldots\II_n$ interface table such that
$\forall\II\in\II_0\ldots\II_n, \II$ OK,\\*
if $\II_0$ has \textbf{@ObjWeak},
$\valid(\C_0)$  and $\QM{of}\notin\dom(\C_0)$,
then in the interface table
$[\![\II_0]\!]\II_1\ldots\II_n$\\*
$\forall\II\in[\![\II_0]\!]\II_1\ldots\II_n$ $\II$ OK.\\

\noindent For convenience, assume that
\begin{align*}
\II_0\ &=\ \weakAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC\\
[\![\II_0]\!]\ &=\ \emptyset\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \method' \cC
\end{align*}

@@

@@

        &\C_i\ \m_i\oR\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\

@@

@@

        &\C_0\ \QM{with#}\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\

@@

        &\C_0\ \QM_\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\

@@

    Here we simply refer to $\valid(\C_0)$, since it guarantees each abstract method to satisfy $\isField$, $\isWith$ or $\isSetter$. But that object includes all implementations for those cases\marco{you need to expand here, proof that we have all the implementations for all cases by using the definition of ofMethod}, hence it is of type $\C_0$ by \rn{t-Obj}.

@@

\subsection{Proof of THEOREM}
\marco{the therem statement must be here}
\label{subsec:proof3}
\begin{proof}
\textbf{LEMMA 2} already proves that $[\![\II_0]\!]$ is OK. On the other hand, for any $\II\ne\II_0$, by \textbf{LEMMA 1}, we know that all its methods
are still well-typed, and the generated code in translation of \textbf{@ObjWeak} is only a static method \QM{of}, which has no way to affect the domain
of $\II$, so after translation rule \rn{t-Intf} can still be applied, which finishes our proof.
\end{proof}

>>>>

@@

    For convenience, we use ``$\method$ in $\ofMethod(\C_0)$'' to denote that $\method$ is one of the implemented methods in the return expression of $\ofMethod(\C_0)$, namely \Q@new@ $\C_0$\Q@(){...}@.

@@

        &\C_i\ \m_i\oR\cR\ \QM{\{...\}}\mbox{ in }\ofMethod(\C_0)\\

@@

        \haoyuan{Right, sorry for that, I mean if a getter is created by ofMethod, then it is a field of I0, and finally for this part our aim is to prove sigvalid, and the definition of sigvalid asks you to prove $\mh\QM;<:\mBody(...)$, see the last line.}

@@

        &\C_0\ \QM{with#}\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{...\}}\mbox{ in }\ofMethod(\C_0)\\

@@

        &\C_0\ \QM_\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{...\}}\mbox{ in }\ofMethod(\C_0)\\

@@

    Here we simply refer to $\valid(\C_0)$, since it guarantees each abstract method to satisfy $\isField$, $\isWith$ or $\isSetter$. But that object includes all implementations for those cases. A getter $m_i$ is generated if it satisfies $\isField$; a \Q@with-@ method is generated for the case $\isWith$, by the definition of $\withMethod$; a setter for $\isSetter$, similarly, by the definition of $\setterMethod$. Hence it is of type $\C_0$ by \rn{t-Obj}.

@@

\subsection{THEOREM and Proof}\label{subsec:theorem}
\textbf{THEOREM. }
For a given $\II_0\ldots\II_n$ interface table such that
$\forall\II\in\II_0\ldots\II_n, \II$ OK,\\*
if $\II_0$ has \textbf{@ObjWeak},
$\valid(\C_0)$  and $\QM{of}\notin\dom(\C_0)$,
then in the interface table
$[\![\II_0]\!]\II_1\ldots\II_n$\\*
$\forall\II\in[\![\II_0]\!]\II_1\ldots\II_n$ $\II$ OK.
\begin{proof}
\textbf{LEMMA 2} already proves that $[\![\II_0]\!]$ is OK. On the other hand, for any $\II\ne\II_0$, by \textbf{LEMMA 1}, we know that all its methods
are still well-typed, and the generated code in translation of \textbf{@ObjWeak} is only a static method \QM{of}, which has no way to affect the domain
of $\II$, so after translation rule \rn{t-Intf} can still be applied, which finishes our proof.
\end{proof}

### 2015-12-02 paper/sections/Translation.tex
Revise formalization and proof.

\subsection{Guaratees}
Now we try to understand what is the meaning of saying that our approach is correct, and more in genera, what it means to say that a Language tuning is correct.
We identify three types of guarancees:
\begin{itemize}
\item \textit{Self coherence}: the generated code itself is well-typed; type errors are not present in code the user have not wrote.
In our case it means that either \mixin{} produces in controlled way an understandable error, or the class can be successfully annotate and the generated code is well typed.
We guarantee \textit{Self coherence}.

\item \textit{Client coherence}: all the client code (as for example method calls) that is well typed without the generation/instrumentation process is well typed also after the generation.
That is, the annotation do not remove any functionality, is just
adding more behaviour.
We guarantee \textit{Client coherence}.

\item \textit{Heir coherence}: Interfaces (and in general classes) inheriting from instrumented code are well typed if they was well typed without the instrumentation.
This would require to not add any (default or abstract) method to the annotated interfaces, including type refinement.
\mixin  do not guarantee \textit{Heir coherence}.
Indeed consider the following example

@@

By the translation rule, \mixin would  generate in \Q@B@  a method ``\Q@B withX(int x);@''.
This would break \Q@C@.
\end{itemize}
\subsection{Results}
Informally, in a type correct interface table, if we translate a specific interface, then
the resulting table is type correct, or there is a subtype of the translated interface in the original table.
\textbf{THEOREM. }
For a given $\II_0\ldots\II_n$ interface table such that
$\forall\II\in\II_0\ldots\II_n, \II$ OK,\\*
if $\II_0$ has \mixin,
$\valid(\C_0)$  and $\QM{of}\notin\dom(\C_0)$,
there is no $\C<:\C_0$, there is no \Q@new @$\C_0$\Q@(){..}@,
then in the interface table
$[\![\II_0]\!]\II_1\ldots\II_n$\\*
$\forall\II\in[\![\II_0]\!]\II_1\ldots\II_n$ $\II$ OK.

@@

To prove the theorem we introduce two lemmas below. The complete proof is available in Appendix \ref{subsec:proof1}, \ref{subsec:proof2} and \ref{subsec:proof3}.\\

\marco{ you need to use the Lemma/theorem macros}
\noindent\textbf{LEMMA 2. }
If $\II_0$ OK, then $[\![\II_0]\!]$ OK.
This is what we defined as self coherence before.

>>>>

\subsection{Guaratees}
Now we try to understand what is the meaning of saying that our approach is correct, and more in general, what it means to say that a language tuning is correct.\haoyuan{Actually only self coherence is supported?}
We identify three types of guarantees:
\begin{itemize}
\item \textit{Self coherence}: the generated code itself is well-typed; type errors are not present in code the user have not wrote.
In our case it means that either \mixin{} produces in controlled way an understandable error, or the class can be successfully annotate and the generated code is well typed.
We guarantee \textit{Self coherence}.

\item \textit{Client coherence}: all the client code (as for example method calls) that is well typed without the generation/instrumentation process is well typed also after the generation.
That is, the annotation do not remove any functionality, is just
adding more behaviour.
\mixin  does not guarantee \textit{Client coherence}.

\item \textit{Heir coherence}: Interfaces (and in general classes) inheriting from instrumented code are well typed if they was well typed without the instrumentation.
This would require to not add any (default or abstract) method to the annotated interfaces, including type refinement.
\mixin  does not guarantee \textit{Heir coherence}.
Indeed consider the following example:

@@

\noindent By the translation rule, \mixin would  generate in \Q@B@  a method ``\Q@B withX(int x);@''.
This would break \Q@C@. And it's similar why client coherence is not supported as well. In the client code, an expression
that uses ``\Q@new B(){...}@'' to create an object of \Q@B@ gives an implementation of \Q@A withX(int x);@, but after the return
type is refined to \Q@B@, there is a type error.
\end{itemize}

\noindent Consequently, type refinement is a common case in client code, and hence is included by \mixin as a feature for convenient use, whereas it simultaneously brings some risk in throwing type errors, though they are likely to be fixed easily by users. On the other hand, a property of \mixin is informally concluded as: for a client program that typechecks before a translation is applied, if the annotated type has no subtypes, and no objects of that type are created, then type safety is guaranteed after the successful translation. Conversely, the second step of \mixin, namely what \Q:@ObjWeak: does in the formalization, is guaranteed to be type-safe for the three kinds of coherence. The formal theorem and proof is presented afterwards.

\subsection{Results}

\haoyuan{We use \textbf{@ObjWeak} or \Q:@ObjWeak:?}

The theorem is presented below. Lemmas and the complete proof are available in Appendix~\ref{subsec:lemma1},~\ref{subsec:lemma2} and~\ref{subsec:theorem}.\\

\noindent\textbf{THEOREM. }
For a given $\II_0\ldots\II_n$ interface table such that
$\forall\II\in\II_0\ldots\II_n, \II$ OK,\\*
if $\II_0$ has \textbf{@ObjWeak},
$\valid(\C_0)$  and $\QM{of}\notin\dom(\C_0)$,
then in the interface table
$[\![\II_0]\!]\II_1\ldots\II_n$\\*
$\forall\II\in[\![\II_0]\!]\II_1\ldots\II_n$ $\II$ OK.

@@
